### 2019-05-28 paper_03_toy_model/article.tex
Safe commands in pandoc preamble to allow for auto width of images, use  to remove width

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=11.5cm]{./fig1.eps}}
 \caption{Spectral energy fluxes as functions of spherical harmonic wave number $ l $, calculated from the AFES GCM. The red solid curve is the KE flux, the blue curve is the APE flux, the black curve is the sum of KE and APE fluxes and the green curve is the accumulated APE-KE conversion. The dotted red curve is the 2D KE flux, calculated only from the rotational part of the velocity field, while the dashed curve is the difference between the total and the 2D KE flux. 
Reprinted
with permission from P. Augier \& E. Lindborg, 
"A new formulation of the spectral energy budget of the atmosphere, with application to two high-resolution general circulation models", 
J. Atmos. Sci. \textbf{70}, 2293--2308 (2013).
Copyright 2013 American Meterological Society.
}
 \label{Flux}
 \end{figure}

@@

Theories that are trying to explain the mesoscale $ k^{-5/3} $ spectrum predict that the three-dimensional structures behind the forward energy cascade are very thin and elongated. \citet{Lindborg:2006} and 
\citet{Waite-Bartello:2004}  emphasise that  it is necessary to have a vertical resolution which is finer than the buoyancy scale, $ \l_b= u/N $, in order to simulate the downscale energy cascade. Here, $ u $ is a characteristic horizontal velocity and $ N $ is the Brunt-V\"sisal\"a frequency. In the upper troposphere and the lower stratosphere $ l_b $ can be estimated to be of the order of one km at most.  According to the hypothesis  of \citet{Callies-Buhler-Ferrari:2016} the mesoscale energy spectrum is built up by inertia-gravity waves with frequencies very close to the inertial frequency $ f $. The ratio between the vertical and the horizontal wave length of such waves is extremely small. With a horizontal wave length $ \lambda_{h} \sim 100 $ km, the corresponding vertical wave length would be a few hundred meters. Despite the prediction of these theories that a very fine resolution would be needed in order to simulate the downscale mesoscale energy cascade it is a fact that GCMs such as the AFES-model and the MPAS-model \citep{Skamarock-Park-Klemp-Snyder:2014} are able to do this although they lack the required vertical resolution. This fact has lead us to the following questions: What is the minimum number of levels that are needed in order to simulate the mesoscale downscale energy cascade? Is it even possible to do this with a single level model, in other words with a two-dimensional model? It is the aim of the present paper to construct such a model.

@@

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=10.5cm]{./fig2.eps}}
 \caption{Spectral energy fluxes from run 1, normalised by the time averaged total energy dissipation $ \epsilon $.  }
 \label{F1}
 \end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=10cm]{./fig4.eps}}
 \caption{Wave energy spectra from simulations with different degrees of the diffusion operator.  }
 \label{Comp1}
 \end{figure}

 \begin{figure}[h]
\centerline{\includegraphics[angle=0,width=17cm]{./fig5.eps}}
 \caption{Energy fluxes from run 1 (left) and run 2 (right) decomposed into different contributions. }
 \label{Flux2}
 \end{figure}

  \begin{figure}[h]
\centerline{\includegraphics[angle=0,width=17 cm]{./fig6.eps}}
 \caption{Compensated wave energy spectra (left) and uncompensated vortical spectra (right) from run 1 and run 2. }
 \label{C2}
 \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=17cm]{./fig7.eps}}
 \caption{Potential enstrophy flux from run 1 (left) and run 2 (right). }
 \label{EF1}
  \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=18.5cm]{./fig8.pdf}}
\caption{Divergence field from a simulation of the shallow water equations (left) and from run 1 of the toy model (right). }
\label{Shocks}
 \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=18.5cm]{./fig9.pdf}}
\caption{Potential vorticity field (left) and wave field (right) from the end state of run 1.}
\label{Vis1}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=10.5cm]{./fig10.eps}}
 \caption{Spectral energy fluxes from run 3, normalised by the time averaged total energy dissipation $ \epsilon $. }
 \label{F2}
 \end{figure}

@@

 \begin{figure}[h]
 \centerline{\includegraphics[angle=0,width=18.5cm]{./fig12.eps}}
\caption{Potential vorticity field (left) and wave field (right) from the end state of run 3.}
 \label{Vis2}
 \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=18.5cm]{./fig13.eps}}
\caption{Blow up of the potential vorticity field (left) of a strong anticyclonic vortex and the corresponding wave field (right). }
\label{Vis3}
\end{figure}

@@

Comparing the spectral energy fluxes from a full GCM shown in Fig.~\ref{Flux} with the corresponding fluxes in Fig.~\ref{F2} from run 3 of the toy model we see that there is a striking similarity. A considerable amount of APE which is forced at large scales is converted into KE. A part of the KE is going into a downscale cascade at $ k > k_f $, while the other part, which is of the same order of magnitude, is going into an upscale cascade at $ k < k_f $. The upscale cascade is restricted to KE and is produced by interactions only involving the rotational component of the velocity field. The downscale energy cascade, on the other hand, is a cascade of both APE and KE. Here we also see an important difference. In the toy model there is perfect equipartition between KE and APE at high wave numbers and also between the fluxes $ \Pi_K $ and $ \Pi_A $. In the GCM, on the other hand, $ \Pi_K > \Pi_A $ at corresponding wave numbers. Clearly, the downscale energy cascade in the GCM is not a clean wave energy cascade with equipartition between KE and APE. \citet{Callies-Ferrari-Buhler:2014} have suggested that the mesoscale $ k^{-5/3} $ spectrum is produced by inertia-gravity waves with frequencies that are close to $ f $. For such waves, $ E_K > E_A $. However, the kinetic energy content in the rotational component of the velocity field is necessarily smaller than in the divergent component, and that is at odds with observational evidence \citep{Lindborg:2015, QiangLi2017}.  There is also numerical evidence \citep{Deusebio-Augier-Lindborg:2013, Asselin2017} suggesting that the forward energy mesoscale energy cascade cannot be described as a cascade of waves at high wave numbers, although it may start as a wave cascade at low wave numbers. In any case, as we pointed out earlier, the forward energy cascade in the GCM cannot be produced by inertia-gravity waves with frequencies close to $ f $, since it would require much finer resolution in the vertical to simulate such motions. Neither can it be fully accounted for by stratified turbulence as suggested by \citet{Lindborg:2006}, since that would also require much finer resolution. In the toy model simulation, on the other hand, we have been able to simulate a downscale energy cascade using only a single level. All nonlinear interactions that are present in the toy-model are also present in the dynamical equations of a full GCM, at each level. Moreover, in the GCM both $ E_A $   and $ E_K $ can be expressed as quadratic quantities to lowest order and the  sum of $ E_A $ and $ E_K $ is approximately conserved. Therefore, it seems likely that the toy model catches the essential cascade dynamics of the GCM. An important difference is, of course, that  inertia-gravity waves in the full GCM, as well as in nature, are three-dimensional, anisotropic and much more dispersive than in the toy model.

@@

%\begin{figure}[h]
%\centerline{\includegraphics[angle=0,width=10.5cm]{./Fig12.eps}}
% \caption{Time averaged potential enstrophy flux from run 2, displayed in a log-log plot. The sign has been reversed in the low wave number range, where the flux is negative (dashed line), implying that potential enstrophy is going both upscale and downscale.  Averaging was made over the intervall $ t/\tau \in [756 \; 1224] $.}
 %\label{EF2}
 % \end{figure}

>>>>

\begin{figure}[h]
\centerline{\includegraphics[angle=0,width=8cm]{./fig1.eps}}
 \caption{Spectral energy fluxes as functions of spherical harmonic wave number $ l $, calculated from the AFES GCM. The red solid curve is the KE flux, the blue curve is the APE flux, the black curve is the sum of KE and APE fluxes and the green curve is the accumulated APE-KE conversion. The dotted red curve is the 2D KE flux, calculated only from the rotational part of the velocity field, while the dashed curve is the difference between the total and the 2D KE flux. 
Reprinted
with permission from P. Augier \& E. Lindborg, 
"A new formulation of the spectral energy budget of the atmosphere, with application to two high-resolution general circulation models", 
J. Atmos. Sci. \textbf{70}, 2293--2308 (2013).
Copyright 2013 American Meterological Society.
}
 \label{Flux}
 \end{figure}

@@

Theories that are trying to explain the mesoscale $ k^{-5/3} $ spectrum predict that the three-dimensional structures behind the forward energy cascade are very thin and elongated. \citet{Lindborg2006} and 
\citet{Waite-Bartello:2004}  emphasise that  it is necessary to have a vertical resolution which is finer than the buoyancy scale, $ \l_b= u/N $, in order to simulate the downscale energy cascade. Here, $ u $ is a characteristic horizontal velocity and $ N $ is the Brunt-V\"sisal\"a frequency. In the upper troposphere and the lower stratosphere $ l_b $ can be estimated to be of the order of one km at most.  According to the hypothesis  of \citet{Callies-Buhler-Ferrari:2016} the mesoscale energy spectrum is built up by inertia-gravity waves with frequencies very close to the inertial frequency $ f $. The ratio between the vertical and the horizontal wave length of such waves is extremely small. With a horizontal wave length $ \lambda_{h} \sim 100 $ km, the corresponding vertical wave length would be a few hundred meters. Despite the prediction of these theories that a very fine resolution would be needed in order to simulate the downscale mesoscale energy cascade it is a fact that GCMs such as the AFES-model and the MPAS-model \citep{Skamarock-Park-Klemp-Snyder:2014} are able to do this although they lack the required vertical resolution. This fact has lead us to the following questions: What is the minimum number of levels that are needed in order to simulate the mesoscale downscale energy cascade? Is it even possible to do this with a single level model, in other words with a two-dimensional model? It is the aim of the present paper to construct such a model.

@@

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig2.eps}}
 \caption{Spectral energy fluxes from run 1, normalised by the time averaged total energy dissipation $ \epsilon $.  }
 \label{F1}
 \end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig4.eps}}
 \caption{Wave energy spectra from simulations with different degrees of the diffusion operator.  }
 \label{Comp1}
 \end{figure}

 \begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig5.eps}}
 \caption{Energy fluxes from run 1 (left) and run 2 (right) decomposed into different contributions. }
 \label{Flux2}
 \end{figure}

  \begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig6.eps}}
 \caption{Compensated wave energy spectra (left) and uncompensated vortical spectra (right) from run 1 and run 2. }
 \label{C2}
 \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig7.eps}}
 \caption{Potential enstrophy flux from run 1 (left) and run 2 (right). }
 \label{EF1}
  \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig8.pdf}}
\caption{Divergence field from a simulation of the shallow water equations (left) and from run 1 of the toy model (right). }
\label{Shocks}
 \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig9.pdf}}
\caption{Potential vorticity field (left) and wave field (right) from the end state of run 1.}
\label{Vis1}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig10.eps}}
 \caption{Spectral energy fluxes from run 3, normalised by the time averaged total energy dissipation $ \epsilon $. }
 \label{F2}
 \end{figure}

@@

 \begin{figure}[h]
 \centerline{\includegraphics[angle=0]{./fig12.eps}}
\caption{Potential vorticity field (left) and wave field (right) from the end state of run 3.}
 \label{Vis2}
 \end{figure}

\begin{figure}[h]
\centerline{\includegraphics[angle=0]{./fig13.eps}}
\caption{Blow up of the potential vorticity field (left) of a strong anticyclonic vortex and the corresponding wave field (right). }
\label{Vis3}
\end{figure}

@@

Comparing the spectral energy fluxes from a full GCM shown in Fig.~\ref{Flux} with the corresponding fluxes in Fig.~\ref{F2} from run 3 of the toy model we see that there is a striking similarity. A considerable amount of APE which is forced at large scales is converted into KE. A part of the KE is going into a downscale cascade at $ k > k_f $, while the other part, which is of the same order of magnitude, is going into an upscale cascade at $ k < k_f $. The upscale cascade is restricted to KE and is produced by interactions only involving the rotational component of the velocity field. The downscale energy cascade, on the other hand, is a cascade of both APE and KE. Here we also see an important difference. In the toy model there is perfect equipartition between KE and APE at high wave numbers and also between the fluxes $ \Pi_K $ and $ \Pi_A $. In the GCM, on the other hand, $ \Pi_K > \Pi_A $ at corresponding wave numbers. Clearly, the downscale energy cascade in the GCM is not a clean wave energy cascade with equipartition between KE and APE. \citet{Callies-Ferrari-Buhler:2014} have suggested that the mesoscale $ k^{-5/3} $ spectrum is produced by inertia-gravity waves with frequencies that are close to $ f $. For such waves, $ E_K > E_A $. However, the kinetic energy content in the rotational component of the velocity field is necessarily smaller than in the divergent component, and that is at odds with observational evidence \citep{Lindborg:2015, QiangLi2017}.  There is also numerical evidence \citep{Deusebio-Augier-Lindborg:2013, Asselin2017} suggesting that the forward energy mesoscale energy cascade cannot be described as a cascade of waves at high wave numbers, although it may start as a wave cascade at low wave numbers. In any case, as we pointed out earlier, the forward energy cascade in the GCM cannot be produced by inertia-gravity waves with frequencies close to $ f $, since it would require much finer resolution in the vertical to simulate such motions. Neither can it be fully accounted for by stratified turbulence as suggested by \citet{Lindborg2006}, since that would also require much finer resolution. In the toy model simulation, on the other hand, we have been able to simulate a downscale energy cascade using only a single level. All nonlinear interactions that are present in the toy-model are also present in the dynamical equations of a full GCM, at each level. Moreover, in the GCM both $ E_A $   and $ E_K $ can be expressed as quadratic quantities to lowest order and the  sum of $ E_A $ and $ E_K $ is approximately conserved. Therefore, it seems likely that the toy model catches the essential cascade dynamics of the GCM. An important difference is, of course, that  inertia-gravity waves in the full GCM, as well as in nature, are three-dimensional, anisotropic and much more dispersive than in the toy model.

@@

%\begin{figure}[h]
%\centerline{\includegraphics[angle=0]{./Fig12.eps}}
% \caption{Time averaged potential enstrophy flux from run 2, displayed in a log-log plot. The sign has been reversed in the low wave number range, where the flux is negative (dashed line), implying that potential enstrophy is going both upscale and downscale.  Averaging was made over the intervall $ t/\tau \in [756 \; 1224] $.}
 %\label{EF2}
 % \end{figure}
